Pillar 1 - Student Topic Profile

### 2019-03-25 Pillar 1 - Topic Profile.Rmd
attach student topic profile to their transcript

```{r}
gamma <- topic_model_gb$g_overview[[10]]
```

```{r}
gamma_spread <- gamma %>% spread(topic, gamma)
```

```{r}
d_transcript_informative %>%

  left_join(gamma_spread, by = c("Course ID" = "document")) %>%
  filter(!is.na(`Topic 1`)) %>%

@@

  group_by(`Student ID`) %>%
  arrange(time) %>% 
  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile of student at time t

  arrange(`Student ID`)
```

>>>>

```{r}
gamma <- topic_model_gb$g_overview[[10]] %>% spread(topic, gamma)
```

```{r}
student_TP <- d_transcript_informative %>%

  left_join(gamma, by = c("Course ID" = "document")) %>%
  filter(!is.na(`Topic 1`)) %>%

@@

  group_by(`Student ID`) %>%
  arrange(time) %>%

  mutate_at(vars(matches("Topic")), lag) %>% # topic profile of student at time t
  mutate_at(vars(matches("Topic")), replace_na, replace = 0) %>% # topic profile of student at time t
  mutate_at(vars(matches("Topic")), cumsum) %>% # topic profile of student at time t

  right_join(d_transcript_informative, by = c("Student ID", "time")) %>%

  select(`Student ID`, `Course ID`, time, everything()) %>%
  arrange(`Student ID`)
```
